In May, the Bank of England's Monetary Policy Committee (MPC) decided to raise the interest rate in response to the exceptionally high inflation of the consumer price index. The committee members were presented with the latest data and thorough analyses conducted by experienced teams of economists. However, the decision was not unanimous: a few members expressed concerns that the contractionary monetary policy shock had not yet been fully internalised, and further rate increases might lead to inflation falling below the target level. Despite this dissent, the majority of the committee members voted in favour of raising the interest rate, considering the potential negative impact of high inflation on households and businesses to outweigh the risks. The meeting minutes effectively demonstrate the informal aspects of the decision-making process. Modern macroeconomic frameworks provide insights into policy objectives and how they can be achieved through fiscal and monetary measures. This dissertation aims to develop a two-country New Keynesian Dynamic Stochastic General Equilibrium (NK DSGE) model for Scotland and the rest of the UK. The model also considers the existence of the world economy and international trading with other countries. The objective of the dissertation is not to build the most factually accurate model tailored to Scotland or the rest of the UK but build a model that would allow an assessment of regional variations in government spending responses under a predefined set of policy scenarios. More specifically, the dissertation considers: a unified fiscal authority scenario in which there exists a single government able to issue bonds and raise taxes and; two autonomous fiscal authorities scenario in which both Scotland and the rest of the UK can issue bonds and raise taxes. Moreover, the dissertation allows fiscal authorities to raise tax revenue by lump-sum or distortionary labour tax. Across all policy scenarios, the model assumes that one monetary authority exists - the Bank of England, and both countries adhere to a UK-wide interest rate. Most model parameters are calibrated in line with the academic literature on DSGE models in the UK. A few model parameters related to government spending and taxes are estimated using Bayesian techniques. Finally, the estimated values are used to derive impulse response functions that are key to delivering the dissertation objectives.

A literature review is presented in the first section. It contrasts the ideas of Keynesian and Classical economists and how their century-long debate lead to the development of the modern macroeconomic frameworks that are used by international organisations and national banks today. The last part of the literature review discusses fiscal policy in DSGE models. The literature review section is followed by a section describing the developed DSGE model. It is split into four parts: households, the government, firms, and equilibrium or market clearing conditions. Given the high number of employed equations by DSGE models, most of the derivations and proofs were put in Appendix, but the accompanying interpretation and intuition are provided in the main text. The fiscal policy parameters are estimated. The Section 3 provides a brief introduction to the Bayesian estimation of the model parameters, data used for estimating fiscal policy parameters, and estimation results. It also lists non-estimated parameters and strategies for calibrating them. The two remaining sections are `Dynamic responses' and `Limitations and Extensions'. The former section analyses dynamic responses of the endogenous variables to two types of shocks: monetary and fiscal. It discusses the effect of government spending when the economy is introduced with a distortionary labour tax, as well as the asymmetry in responses when Scotland is considered fiscally autonomous. This section also provides a parameter sensitivity analysis - a demonstration and a discussion on how the dynamic responses vary given different sets of parameters The limitations section discusses ways the model could be extended to allow more sophisticated policy analysis or an improved data fit. The conclusion summarises all sections of the dissertation and reiterates key findings.